\section{Component interfaces}\label{componentInterfaces}
Here we present the interfaces of our components: in particular which operations they offer, their meaning and their input/output parameters.
\subsection{Account Manager}
\subsubsection{\underline{Passenger}}
\begin{itemize}
	\item \texttt{Passenger login(String username, String password)}\\
	Given valid credentials, allows the passenger to receive a session and to login.
	\item \texttt{void logout(Passenger passenger)}\\
	Given a valid session, it deletes it.
	\item \texttt{boolean register(String username, String password)}\\
	It creates a new account for a passenger with the credentials provided.
	\item \texttt{boolean deleteAccount(String username, String password)}\\
	Given valid credentials, it deletes the account associated.
\end{itemize}
\subsubsection{\underline{TaxiDriver}}
\begin{itemize}
	\item \texttt{TaxiDriver login(String username, String password)}\\
	Given valid credentials, allows the taxi driver to receive a session and to login.
	\item \texttt{void logout(TaxiDriver taxiDriver)}\\
	Given a valid session, it deletes it.
\end{itemize}
\subsection{Ride Manager}
\subsubsection{\underline{RideH
		andler}}
\begin{itemize}
	\item \texttt{Response makeRequest(Location location, int numberOfPassengers,\\ Passenger passenger)}\\
	It starts the activity of making a request. It returns either informations about the taxi driver who is coming, or an invitation to try later.
	\item \texttt{Response makeReservation(Location source, Location destination, \\ int numberOfPassengers, Date date, Time time, Passenger passenger)}\\
	It starts the activity of making a reservation. If the time of the reservation is at least 2 hours later, it return a positive message.
	\item \texttt{List<Reservation> getReservations(Passenger passenger)}\\
	It returns all the reservations of a given passenger.
	\item \texttt{boolean deleteReservation(Passenger passenger, Reservation reservation)}\\
	It deletes a reservation of a passenger.
\end{itemize}
\subsection{Taxi Manager}
\subsubsection{\underline{StatusHandler}}
\begin{itemize}
	\item \texttt{boolean setAvailabilityStatus(TaxiDriver taxiDriver, AvailabilityStatus status)}\\
	It assigns a new availability status to a taxi driver.
	\item \texttt{void setLocation(TaxiDriver taxiDriver, Location location)}\\
	It updates the location of a taxi driver.
\end{itemize}
\subsubsection{\underline{TaxiProvider}}
\begin{itemize}
	\item \texttt{Response provideTaxi(Location location)}\\
	Given a valid location, if there is at least one available taxi driver, it returns it.
\end{itemize}
\subsection{Geographic Engine}
\subsubsection{\underline{ZoneLocator}}
\begin{itemize}
	\item \texttt{Zone getTaxiZone(Location location)}\\
	It computes the corresponding zone of a given location.
	\item \texttt{List<Zone> getTaxiZones()}\\
	It returns all the zones.
	\item \texttt{boolean isValidLocation(Location location)}\\
	Given a location, it checks whether it is valid or not.
\end{itemize}
\subsubsection{\underline{TimeCalculator}}
\begin{itemize}
	\item \texttt{Time getTimeEstimation(Location source, Location, destination)}\\
	Given valid source and valid location, it returns an approximative traveling time.
\end{itemize}
\subsection{Queue Manager}
\subsubsection{\underline{TaxiManagement}}
\begin{itemize}
	\item \texttt{void addTaxi(TaxiDriver taxi, Zone zone)}\\
	Given a taxi driver and a zone, it adds the taxi driver to the queue corresponding to the zone.
	\item \texttt{TaxiDriver getTaxi(Zone zone)}\\
	It returns the first available taxi from the queue corresponding of the given zone.
	\item \texttt{void removeTaxi(TaxiDriver taxi)}\\
	Given a taxi driver, it removes it from the queue he is in.
	\item \texttt{void changeZone(TaxiDriver taxi, Zone zone)}\\
	Given a taxi driver and a zone, it remove the taxi driver from the queue he is in, and add it in the queue corresponding to the zone.
\end{itemize}